A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-01-29 paper.tex
Edits to diagrams & tables

\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{.32\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] (root){}
                child {node [circle,draw] {}
                    child {node [circle,draw] {}
                        edge from parent [fixed] node [left] {$b$}
                    }
                    edge from parent [fixed] node [left] {$a$}
                }
                child {node [circle,draw] {}
                    child {node [circle,draw,right=5pt] {}
                        edge from parent [fixed] node [left] {$e$}
                    }
                    child {node [circle,draw,left=5pt] {}
                        edge from parent [fixed] node [right] {$f$}
                    }
                    edge from parent [fixed] node [right] {$d$}
                }
                node [above=4pt] {$\langle s, 2 \rangle$};
        \end{tikzpicture}
        \caption{A losing AGT $T$}
        \label{fig:interpolatetree}
    \end{subfigure}%
    \begin{subfigure}[t]{.32\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] (root){}
                child {node [circle,draw] {}
                    edge from parent [fixed] node [left] {$a$}
                }
                child {node [circle,draw] {}
                    child {node [circle,draw,right=5pt] {}
                        edge from parent [fixed] node [left] {$e$}
                    }
                    child {node [circle,draw,left=5pt] {}
                        edge from parent [fixed] node [right] {$f$}
                    }
                    edge from parent [fixed] node [right] {$d$}
                }
                node [above=4pt] {$\langle s, 2 \rangle$};
        \end{tikzpicture}
        \caption{Tree slice $T_1$}
        \label{fig:treef1}
    \end{subfigure}%
    \begin{subfigure}[t]{.32\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] {}
                child {node [circle,draw] {}
                    edge from parent [fixed] node [left] {$b$}
                };
%%%                node [above=4pt] {$\langle s', 1 \rangle$};
        \end{tikzpicture}
        \caption{Tree slice $T_2$}
        \label{fig:treef2}
    \end{subfigure}
    \caption{Splitting of an abstract game tree by the learning procedure.}
\end{figure}

@@

\begin{table}
    \centering
    \setlength{\tabcolsep}{8pt}
    \begin{tabular}{l | r | r }
        \textbf{Solver} & \textbf{Solved} & \textbf{Unique} \\
        \hline
        Simple BDD Solver (2) & 195 & 10 \\
        AbsSynthe (seq2) & 187 & 2 \\
        Simple BDD Solver (1) & 185 & \\
        AbsSynthe (seq3) & 179 & \\
        Realizer (sequential) & 179 & \\
        AbsSynthe (seq1) & 173 & 1 \\
        Demiurge (D1real) & 139 & 5 \\
        Aisy & 98 & \\
        \hline
        Unbounded Synthesis & 103 & 12 \\
    \end{tabular}
    \caption{Synthesis Competition 2015 Results}
    \label{tab:syntcomp}
\end{table}

@@

\begin{table}[h]
    \centering
    \setlength{\tabcolsep}{16pt}
    \begin{tabular}{l l}
        \texttt{6s216rb0\_c0to31} & \texttt{driver\_c10n} \\
        \texttt{cnt30y} &  \texttt{stay18y} \\
        \texttt{driver\_a10n} & \texttt{stay20n} \\
        \texttt{driver\_a8n} & \texttt{stay20y} \\
        \texttt{driver\_b10y} & \texttt{stay22n} \\
        \texttt{driver\_b8y} & \texttt{stay22y} \\
    \end{tabular}
    \caption{Instances uniquely solved by our approach}
    \label{tab:unique}
\end{table}

>>>>

\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{.32\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] (root){}
                child {node [circle,draw] {}
                    child {node [circle,draw] {}
                        edge from parent [fixed] node [left] {$b$}
                    }
                    edge from parent [fixed] node [left] {$a$}
                }
                child {node [circle,draw] (n) {}
                    child {node [circle,draw,right=5pt] {}
                        edge from parent [fixed] node [left] {$e$}
                    }
                    child {node [circle,draw,left=5pt] {}
                        edge from parent [fixed] node [right] {$f$}
                    }
                    edge from parent [fixed] {node [right] {$d$}}
                }
                node [above=4pt] {$\langle s, 2 \rangle$};
            \node [right=1pt of n] {$n$};
        \end{tikzpicture}
        \caption{A losing AGT $T$}
        \label{fig:interpolatetree}
    \end{subfigure}%
    \begin{subfigure}[t]{.32\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] (root){}
                child {node [circle,draw] {}
                    edge from parent [fixed] node [left] {$a$}
                }
                child {node [circle,draw] (n) {}
                    child {node [circle,draw,right=5pt] {}
                        edge from parent [fixed] node [left] {$e$}
                    }
                    child {node [circle,draw,left=5pt] {}
                        edge from parent [fixed] node [right] {$f$}
                    }
                    edge from parent [fixed] node [right] {$d$}
                }
                node [above=4pt] {$\langle s, 2 \rangle$};
            \node [right=1pt of n] {$n$};
        \end{tikzpicture}
        \caption{Tree slice $T_1$}
        \label{fig:treef1}
    \end{subfigure}%
    \begin{subfigure}[t]{.32\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] {}
                child {node [circle,draw,right=5pt] {}
                    edge from parent [fixed] node [left] {$e$}
                }
                child {node [circle,draw,left=5pt] {}
                    edge from parent [fixed] node [right] {$f$}
                }
                node [right=5pt] {$n$};
        \end{tikzpicture}
        \caption{Tree slice $T_2$}
        \label{fig:treef2}
    \end{subfigure}
    \caption{Splitting of an abstract game tree by the learning procedure.}
\end{figure}

@@

\begin{table}
    \centering
    \setlength{\tabcolsep}{8pt}
    \begin{tabular}{l | r | r }
        \textbf{Solver} & \textbf{Solved} & \textbf{Unique} \\
        \hline
        Simple BDD Solver (2) & 195 & 10 \\
        AbsSynthe (seq2) & 187 & 2 \\
        Simple BDD Solver (1) & 185 & \\
        AbsSynthe (seq3) & 179 & \\
        Realizer (sequential) & 179 & \\
        AbsSynthe (seq1) & 173 & 1 \\
        Demiurge (D1real) & 139 & 5 \\
        Aisy & 98 & \\
        \textit{Unbounded Synthesis} & \textit{103} & \textit{12} \\
    \end{tabular}
    \caption{Synthesis Competition 2015 Results}
    \label{tab:syntcomp}
\end{table}

@@

\begin{table}[h]
    \centering
    \setlength{\tabcolsep}{16pt}
    \begin{tabular}{l l}
        1. \texttt{6s216rb0\_c0to31} & 7. \texttt{driver\_c10n} \\
        2. \texttt{cnt30y} &  8. \texttt{stay18y} \\
        3. \texttt{driver\_a10n} & 9. \texttt{stay20n} \\
        4. \texttt{driver\_a8n} & 10. \texttt{stay20y} \\
        5. \texttt{driver\_b10y} & 11. \texttt{stay22n} \\
        6. \texttt{driver\_b8y} & 12. \texttt{stay22y} \\
    \end{tabular}
    \caption{Instances uniquely solved by our approach}
    \label{tab:unique}
\end{table}
